Fluid structure interaction with ETVF

### 2021-12-23 manuscript/paper.tex
Improved elastic wedge entry

%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/good_vs_bad}
  \caption{Hydrostatic water column on an elastic plate}
\label{fig:hs-water-on-plate}
\end{figure}
%
%

The simulation is ran for a total time of 0.4 s. For convergence study, three
different particle resolutions, respectively
$h_e / delta_x = 10, h_e / delta_x = 10, h_e / delta_x = 10 $are adopted,
whose respective total number of particles are 1122232 and 1122323. The time
step of the fluid and solid phase are computed separately, but we use
substepping to update the fluid and solid phases as per section
\ref{section:substepping}.

%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/good_vs_bad}
  \caption{Hydrostatic water column on an elastic plate}
\label{fig:hs-water-on-plate}
\end{figure}
%
%

@@

>>>>

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/schematic_t_0.0}}}
  \caption{Hydrostatic water column on an elastic plate}
\label{fig:hs-water-on-plate}
\end{figure}

%

The simulation is ran for a total time of 0.4 s. For convergence study, three
different particle resolutions, respectively $d0 = 0.55 \times 10^{-2}$ m,
$0.35 \times 10^{-2}$ m, $0.25 \times 10^{-2}$ m, are adopted, which generates
10, 20 and 30 particles in along the width direction on the structure
respectively. The test case is ran for a period of 0.3 seconds with 1232233
particles for the highest resolution. The time step of the fluid and solid phase
are computed separately as per equation \eqref{eq:time_step}, but we use
substepping to update the fluid and solid phases as per section
\ref{section:substepping}.

%
\begin{figure}[!htpb]
  \centering
%
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=0.7\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/snap_t_0.3}}}
  \end{subfigure}
%
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=0.3\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/colorbar_t_0.0}}}
  \end{subfigure}
  \caption{Pressure and stress distribution in an hydrostatic tank example}
\label{fig:ng2020hsplate:t_0.3}
\end{figure}
%

%
\begin{figure}[!htpb]
  \centering
%
  \begin{subfigure}{0.8\textwidth}
    \centering
    \includegraphics[width=1\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/y_amplitude}}}
  \end{subfigure}
  \caption{The mid-span deflection of the structure with time}
\label{fig:ng2020hsplate:deflection}
\end{figure}
%

@@

% %
%   \begin{subfigure}{0.24\textwidth}
%     \centering
%     \includegraphics[width=0.7\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/snap_t_0.2}}}
%     \subcaption{t = 4e-03 sec}\label{fig:rings:sun2019-nu-0.3975-2}
%   \end{subfigure}
% %
%   \begin{subfigure}{0.24\textwidth}
%     \centering
%     \includegraphics[width=0.7\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/snap_t_0.2}}}
%     \subcaption{t = 7.3e-03 sec}\label{fig:rings:sun2019-nu-0.3975-3}
%   \end{subfigure}
% %
%   \begin{subfigure}{0.24\textwidth}
%     \centering
%     \includegraphics[width=0.7\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/colorbar_t_0.0}}}
%     % \subcaption{t = 1.45e-02 sec}\label{fig:rings:sun2019-nu-0.3975-4}
%   \end{subfigure}
% % %
% %   \begin{subfigure}{0.3\textwidth}
% %     \centering
% %     \includegraphics[width=1.0\textwidth]{figures/rings/etvf_sun2019_poisson_ratio_0.3975/time5}
% %     \subcaption{t = 1.5e-02 sec}\label{fig:rings:sun2019-nu-0.3975-5}
% %   \end{subfigure}

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.8\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/schematic_t_0.0}}}
  \caption{Dam breaking on to an elastic obstacle}
\label{fig:dambreak-onto-a-plate}
\end{figure}

%

\begin{figure}[!htpb]
  \centering
%
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.0}}}
  \end{subfigure}
%
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.2}}}
  \end{subfigure}

  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.4}}}
  \end{subfigure}
%
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.5}}}
  \end{subfigure}

  \begin{subfigure}{0.4\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.6}}}
  \end{subfigure}
%
  \begin{subfigure}{0.4\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.7}}}
  \end{subfigure}
%
  \begin{subfigure}{0.09\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/colorbar_t_0.0}}}
  \end{subfigure}

  \caption{Pressure and stress distribution in dam breaking onto a elastic
    obstacle case}
  \label{fig:sun2019dambreakobstable}
\end{figure}
%

\begin{figure}[!htpb]
  \centering
%
  \begin{subfigure}{0.8\textwidth}
    \centering
    \includegraphics[width=1\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/x_amplitude}}}
  \end{subfigure}
  \caption{The mid-span deflection of the structure with time}
\label{fig:ng2020hsplate:deflection}
\end{figure}
%
\FloatBarrier%
